---
title: "Authentification"
author: "Maggie Klope"
date: "3/19/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Authentification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

getissues works for personal and Enterprise GitHub repos, but requires the use of GitHub Personal Authentication Token (PATs) for access.

This can be done in a number of ways, but one of the most secure ways is to set up an encrypted file, especially if you are working on a shared computer or server or sharing your code.

Below we illustrate how to save your PAT using the [keyring package](https://cran.r-project.org/web/packages/keyring/index.html).

The first step is to obtain a token from GitHub following the guide outlined [here](https://docs.github.com/en/github/authenticating-to-github/creating-a-personal-access-token)

Next, create a new keyring backend:
```{r}
# kb <- backend_file$new()
```

Then, set a password for you keyring. Enter the password in the new window when prompted.
This only needs to be run once.
```{r}
# kb$keyring_create("Git_Credentials")
```

Next, use your password to unlock the keyring when prompted.
```{r}
# kb$keyring_unlock("Git_Credentials")
```

Now you can save your PAT and credentials within the keyring.  Each keyring can contain many keys, which is are defined by their service name and password.
```{r}
# # Repos on an Enterprise account must be named "Github_Enterprise_Token"
# kb$set(service = "Github_Enterprise_Token", username = "username", keyring = "Git_Credentials")
```

Finally, lock your keyring
```{r}
# kb$keyring_lock("Git_Credentials") 
```

Now you can access your PAT safely through your keyring when using the gitissues package setting the PAT argument to.
```{r}
# get_issues(github_api_endpoint = "/repos/owner/repo/issues",
#            url = "https:://api.github.com",
#            repo_owner = "owner",
#            repo_name = "repo",
#            PAT = kb$get("Github_Enterprise_Token", keyring = "Git_Credentials"))

```
